---
output:
  html_document: default
  pdf_document: default
---

# STAT 349 Final Project Report
### Kenny Jin

```{r}
library(tseries)
library(TSA)
```

Note: log based 10 is always used in this project
Some of the dataset is replaced because of the length.
Current datasets (\* means replaced):

\*BLL
F
\*LLY
LOW
MCO
MSFT
PFE
ROK
\*TRV
\*TXT


```{r}
library(readxl)    
read_excel_allsheets <- function(filename, tibble = FALSE) {
    # I prefer straight data.frames
    # but if you like tidyverse tibbles (the default with read_excel)
    # then just pass tibble = TRUE
    sheets <- readxl::excel_sheets(filename)
    x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X))
    if(!tibble) x <- lapply(x, as.data.frame)
    names(x) <- sheets
    x
}
mysheets <- read_excel_allsheets("KennyJin.xlsx")
```

```{r}
select_best_model <- function(data, max_p=2, max_q=2) {
  min_ssr <- Inf
  best_param <- c(-1, -1)
  best_model <- NULL
  # Find the model with the smallest sum square of residuals
  for (p in 1:max_p) {
    for (q in 1:max_q) {
      capture.output(model <- garch(x=data,order=c(p,q)))
      ssr <- sum(na.omit(model$residuals)^2)
      if (ssr < min_ssr) {
        min_ssr <- ssr
        best_param <- c(p, q)
        best_model <- model
      }
    }
  }
  print(min_ssr)
  print(best_param)
  return(best_param)
}
```



# 1 Steps 1-3

## 1.1 Dataset 1: Stock BLL

```{r}
BLL = mysheets$BLL
BLL.return = na.omit(BLL$`Log Return`)
```


### 1.1.1 

```{r}
# prints ssr and best parameters
best_params <- select_best_model(BLL.return)
```



```{r}
o = capture.output(mpq <- garch(x=BLL.return,order=best_params))
```

```{r}
summary(mpq)
```


The best fitted model is GARCH(1,2) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model.

GARCH(1,2) gives the smallest sum of squared residuals for this dataset.

### 1.1.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```


```{r}
par(mfrow=c(1,2))
plot(BLL$Date[-1], BLL.return, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

Figure: The left panel is the log return original series from 01/04/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```


Figure: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

```{r}
BLL.residual=na.omit(residuals(mpq))
```


## 1.2-1.10 Same as 1.1

## 1.2 Dataset 1: Stock F

```{r}
F = mysheets$F
F.return = na.omit(F$`Log Return`)
```


### 1.2.1 

```{r}
# prints ssr and best parameters
best_params <- select_best_model(F.return)
```



```{r}
o = capture.output(mpq <- garch(x=F.return,order=best_params))
```

```{r}
summary(mpq)
```


The best fitted model is GARCH(1,2) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model.

GARCH(1,2) gives the smallest sum of squared residuals for this dataset.

### 1.2.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```


```{r}
par(mfrow=c(1,2))
plot(F$Date[-1], F.return, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

Figure: The left panel is the log return original series from 01/04/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```


Figure: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

```{r}
F.residual=na.omit(residuals(mpq))
```

## 1.3 Dataset 1: Stock LLY

```{r}
LLY = mysheets$LLY
LLY.return = na.omit(LLY$`Log Return`)
```


The original log return series is plotted in Figure on the left panel. The fitted
residuals (standardized returns or pseudo-returns) are plotted on the right panel.

### 1.3.1 

```{r}
# prints ssr and best parameters
best_params <- select_best_model(LLY.return)
```



```{r}
o = capture.output(mpq <- garch(x=LLY.return,order=best_params))
```

```{r}
summary(mpq)
```


The best fitted model is GARCH(1,2) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model.

GARCH(1,2) gives the smallest sum of squared residuals for this dataset.

### 1.3.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```


```{r}
par(mfrow=c(1,2))
plot(LLY$Date[-1], LLY.return, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

Figure: The left panel is the log return original series from 01/04/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```

Figure: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

```{r}
LLY.residual=na.omit(residuals(mpq))
```

## 1.4 Dataset 1: Stock LOW

```{r}
LOW = mysheets$LOW
LOW.return = na.omit(LOW$`Log Return`)
```


The original log return series is plotted in Figure on the left panel. The fitted
residuals (standardized returns or pseudo-returns) are plotted on the right panel.

### 1.4.1 

```{r}
# prints ssr and best parameters
best_params <- select_best_model(LOW.return)
```



```{r}
o = capture.output(mpq <- garch(x=LOW.return,order=best_params))
```

```{r}
summary(mpq)
```


The best fitted model is GARCH(2,2) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model.

GARCH(2,2) gives the smallest sum of squared residuals for this dataset.

### 1.4.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```


```{r}
par(mfrow=c(1,2))
plot(LOW$Date[-1], LOW.return, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

Figure: The left panel is the log return original series from 01/04/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```


Figure: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

```{r}
LOW.residual=na.omit(residuals(mpq))
```

## 1.5 Dataset 1: Stock MCO

```{r}
MCO = mysheets$MCO
MCO.return = na.omit(MCO$`Log Return`)
```


The original log return series is plotted in Figure on the left panel. The fitted
residuals (standardized returns or pseudo-returns) are plotted on the right panel.

### 1.5.1 

```{r}
# prints ssr and best parameters
best_params <- select_best_model(MCO.return)
```



```{r}
o = capture.output(mpq <- garch(x=MCO.return,order=best_params))
```

```{r}
summary(mpq)
```


The best fitted model is GARCH(1,2) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model.

GARCH(1,2) gives the smallest sum of squared residuals for this dataset.

### 1.5.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```


```{r}
par(mfrow=c(1,2))
plot(MCO$Date[-1], MCO.return, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

Figure: The left panel is the log return original series from 01/04/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```


Figure: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

```{r}
MCO.residual=na.omit(residuals(mpq))
```

## 1.6 Dataset 1: Stock MSFT

```{r}
MSFT = mysheets$MSFT
MSFT.return = na.omit(MSFT$`Log Return`)
```


The original log return series is plotted in Figure on the left panel. The fitted
residuals (standardized returns or pseudo-returns) are plotted on the right panel.

### 1.6.1 

```{r}
# prints ssr and best parameters
best_params <- select_best_model(MSFT.return)
```



```{r}
o = capture.output(mpq <- garch(x=MSFT.return,order=best_params))
```

```{r}
summary(mpq)
```


The best fitted model is GARCH(1,2) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model.

GARCH(1,2) gives the smallest sum of squared residuals for this dataset.

### 1.6.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```


```{r}
par(mfrow=c(1,2))
plot(MSFT$Date[-1], MSFT.return, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

Figure: The left panel is the log return original series from 01/04/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```


Figure: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

```{r}
MSFT.residual=na.omit(residuals(mpq))
```

## 1.7 Dataset 1: Stock PFE

```{r}
PFE = mysheets$PFE
PFE.return = na.omit(PFE$`Log Return`)
```


The original log return series is plotted in Figure on the left panel. The fitted
residuals (standardized returns or pseudo-returns) are plotted on the right panel.

### 1.7.1 

```{r}
# prints ssr and best parameters
best_params <- select_best_model(PFE.return)
```



```{r}
o = capture.output(mpq <- garch(x=PFE.return,order=best_params))
```

```{r}
summary(mpq)
```


The best fitted model is GARCH(1,2) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model.

GARCH(1,2) gives the smallest sum of squared residuals for this dataset.

### 1.7.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```


```{r}
par(mfrow=c(1,2))
plot(PFE$Date[-1], PFE.return, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

Figure: The left panel is the log return original series from 01/04/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```


Figure: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

```{r}
PFE.residual=na.omit(residuals(mpq))
```

## 1.8 Dataset 1: Stock ROK

```{r}
ROK = mysheets$ROK
ROK.return = na.omit(ROK$`Log Return`)
```


The original log return series is plotted in Figure on the left panel. The fitted
residuals (standardized returns or pseudo-returns) are plotted on the right panel.

### 1.8.1 

```{r}
# prints ssr and best parameters
best_params <- select_best_model(ROK.return)
```



```{r}
o = capture.output(mpq <- garch(x=ROK.return,order=best_params))
```

```{r}
summary(mpq)
```


The best fitted model is GARCH(2,1) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model.

GARCH(1,2) gives the smallest sum of squared residuals for this dataset.

### 1.8.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```


```{r}
par(mfrow=c(1,2))
plot(ROK$Date[-1], ROK.return, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

Figure: The left panel is the log return original series from 01/04/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```

Figure: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

```{r}
ROK.residual=na.omit(residuals(mpq))
```

## 1.9 Dataset 1: Stock TRV

```{r}
TRV = mysheets$TRV
TRV.return = na.omit(TRV$`Log Return`)
```


The original log return series is plotted in Figure on the left panel. The fitted
residuals (standardized returns or pseudo-returns) are plotted on the right panel.

### 1.9.1 

```{r}
# prints ssr and best parameters
best_params <- select_best_model(TRV.return)
```



```{r}
o = capture.output(mpq <- garch(x=TRV.return,order=best_params))
```

```{r}
summary(mpq)
```


The best fitted model is GARCH(1,2) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model.

GARCH(1,2) gives the smallest sum of squared residuals for this dataset.

### 1.9.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```


```{r}
par(mfrow=c(1,2))
plot(TRV$Date[-1], TRV.return, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

Figure: The left panel is the log return original series from 01/04/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```


Figure: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

```{r}
TRV.residual=na.omit(residuals(mpq))
```

## 1.10 Dataset 1: Stock TXT

```{r}
TXT = mysheets$TXT
TXT.return = na.omit(TXT$`Log Return`)
```


The original log return series is plotted in Figure on the left panel. The fitted
residuals (standardized returns or pseudo-returns) are plotted on the right panel.

### 1.10.1 

```{r}
# prints ssr and best parameters
best_params <- select_best_model(TXT.return)
```



```{r}
o = capture.output(mpq <- garch(x=TXT.return,order=best_params))
```

```{r}
summary(mpq)
```


The best fitted model is GARCH(1,2) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model.

GARCH(1,2) gives the smallest sum of squared residuals for this dataset.

### 1.10.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```


```{r}
par(mfrow=c(1,2))
plot(TXT$Date[-1], TXT.return, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```

Figure: The left panel is the log return original series from 01/04/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```


Figure: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

```{r}
TXT.residual=na.omit(residuals(mpq))
```


```{r}
# Gather model redisuals into a data frame
mpq_residuals = data.frame(BLL.residual, F.residual, LLY.residual, LOW.residual, MCO.residual, MSFT.residual, PFE.residual, ROK.residual, TRV.residual, TXT.residual)
# Get log return dataframe and closing price dataframe for all 10 companies
all_logret = mysheets$LOGRET
all_price = mysheets$PRICE
```


# 2 Step 5

```{r}
c_1 = rep(1/10, 10)
c_best = rep(0, 10)
```


1. Report the sample mean and sample standard deviation ($c_i=1/10$) of $r_t$.

```{r}
# Compute r_t for c_i=1/10
rt.c1 = as.numeric(data.matrix(all_logret) %*% matrix(c_1, nrow=10, ncol=1))
```

```{r}
cat('mean: ',mean(rt.c1), '\n')
cat('standard deviation: ', sd(rt.c1))
```

```{r}
# Alternative way to compute mean of r_t
# sum(colSums(all_logret) * c_1)/3829
```


2. Report the sample mean and sample standard deviation ($c_i=?$) of $r_t$.

```{r}
library(Surrogate)
```


```{r}
best_mean = mean(rt.c1)
best_sd = sd(rt.c1)
c_best = c_1
set.seed(30)
for (i in 1:50000){
  c_curr = as.numeric(RandVec(a=0, b=1, s=1, n=10, m=1, Seed=sample(1:2147483647, size = 1))$`RandVecOutput`)
  
  rt.curr = as.numeric(data.matrix(all_logret) %*% matrix(c_curr, nrow=10, ncol=1))
  curr_mean = mean(rt.curr)
  curr_sd = sd(rt.curr)
  if (curr_mean > best_mean && curr_sd <= best_sd) {
    best_mean = curr_mean
    best_sd = curr_sd
    c_best = c_curr
  }
}

cat('c_best: ', c_best, '\n')
cat('mean: ',best_mean, '\n')
cat('standard deviation: ', best_sd)

```

```{r}
# Compute r_t for c_best
# rt.cbest = as.numeric(data.matrix(all_logret) %*% matrix(c_best, nrow=10, ncol=1))
```


3. Report your optimization procedure.

I used Monte Carlo method to simulate the best c vector. I generated a lot of c vectors $c(c_1,c_2,...,c_{10})$ that are uniformly distributed in the space where $c_1+c_2+...+c_{10}=1$ and $c_i\geq0$. I select the best c vector which generates the largest objective value and satisfy the condition that the std smaller than or equal to the std from c(1/10).

# 3 Step 6

1. Report the sample mean and sample standard deviation ($c_i=1/10$) of $r_t^\epsilon$.

```{r}
# Compute r_t^epsilon for c_i=1/10
rtep.c1 = as.numeric(data.matrix(mpq_residuals) %*% matrix(c_1, nrow=10, ncol=1))
```

```{r}
cat('mean: ',mean(rtep.c1), '\n')
cat('standard deviation: ', sd(rtep.c1))
```

2. Report the sample mean and sample standard deviation ($c_i=?$) of $r_t^\epsilon$.

```{r}
best_mean = mean(rtep.c1)
best_sd = sd(rtep.c1)
c_best = c_1
set.seed(10)
for (i in 1:50000){
  c_curr = as.numeric(RandVec(a=0, b=1, s=1, n=10, m=1, Seed=sample(1:2147483647, size = 1))$`RandVecOutput`)
  
  rtep.curr = as.numeric(data.matrix(mpq_residuals) %*% matrix(c_curr, nrow=10, ncol=1))
  curr_mean = mean(rtep.curr)
  curr_sd = sd(rtep.curr)
  if (curr_mean > best_mean && curr_sd <= best_sd) {
    best_mean = curr_mean
    best_sd = curr_sd
    c_best = c_curr
  }
}

cat('c_best: ', c_best, '\n')
cat('mean: ',best_mean, '\n')
cat('standard deviation: ', best_sd)

```

```{r}
# Compute r_t for c_best
# rt.cbest = as.numeric(data.matrix(mpq_residuals) %*% matrix(c_best, nrow=10, ncol=1))
```



3. Report your optimization procedure.

I used Monte Carlo method to simulate the best c vector. I generated a lot of c vectors $c(c_1,c_2,...,c_{10})$ that are uniformly distributed in the space where $c_1+c_2+...+c_{10}=1$ and $c_i\geq0$. I select the best c vector which generates the largest objective value and satisfy the condition that the std smaller than or equal to the std from c(1/10).


# 4 Step 7

```{r}
# this is to compute r_t^p based on c_1
# V is an intermediate vector for computation
V = as.numeric(data.matrix(all_price) %*% matrix(c_1, nrow=10, ncol=1))
rtp.c1 = log10(V[-1]) - log10(V[-length(V)])
```


1. Report the sample mean and sample standard deviation ($c_i=1/10$) of $r_t^p$.

```{r}
cat('mean: ',mean(rtp.c1), '\n')
cat('standard deviation: ', sd(rtp.c1))
```


2. Report the sample mean and sample standard deviation ($c_i=?$) of $r_t^p$.

```{r}
best_mean = mean(rtp.c1)
best_sd = sd(rtp.c1)
c_best = c_1
set.seed(20)
for (i in 1:50000){
  c_curr = as.numeric(RandVec(a=0, b=1, s=1, n=10, m=1, Seed=sample(1:2147483647, size = 1))$`RandVecOutput`)
  
  V = as.numeric(data.matrix(all_price) %*% matrix(c_curr, nrow=10, ncol=1))
  rtp.curr = log10(V[-1]) - log10(V[-length(V)])
  curr_mean = mean(rtp.curr)
  curr_sd = sd(rtp.curr)
  if (curr_mean > best_mean && curr_sd <= best_sd) {
    best_mean = curr_mean
    best_sd = curr_sd
    c_best = c_curr
  }
}

cat('c_best: ', c_best, '\n')
cat('mean: ',best_mean, '\n')
cat('standard deviation: ', best_sd)

```

```{r}
# this is to compute r_t^p based on c_1
# V is an intermediate vector for computation
V = as.numeric(data.matrix(all_price) %*% matrix(c_best, nrow=10, ncol=1))
rtp.cbest = log10(V[-1]) - log10(V[-length(V)])
```


3. Report your optimization procedure.

I used Monte Carlo method to simulate the best c vector. I generated a lot of c vectors $c(c_1,c_2,...,c_{10})$ that are uniformly distributed in the space where $c_1+c_2+...+c_{10}=1$ and $c_i\geq0$. I select the best c vector which generates the largest objective value and satisfy the condition that the std smaller than or equal to the std from c(1/10).


# 5 Step 8

## 5.1 Dataset: 

$r_t^p$ from $c_i=1/10$

```{r}
# prints ssr and best parameters
best_params <- select_best_model(rtp.c1)
```

### 5.1.1 

The best fitted model is GARCH(p,q) with the following estimated parameter values and standard errors.

```{r}
o = capture.output(mpq <- garch(x=rtp.c1,order=best_params))
summary(mpq)
```


Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model, instead of GARCH(1,2),
GARCH(2,1), or GARCH(2,2).

### 5.1.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
cat('skewness: ', skewness(na.omit(residuals(mpq))), '\n')
cat('kurtosis: ', kurtosis(na.omit(residuals(mpq))))
```



```{r}
par(mfrow=c(1,2))
plot(TXT$Date[-2], rtp.c1, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```


Figure 5.1: The left panel is the log return original series from 01/05/2005 to
03/20/2020. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```


Figure 5.2: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

1. Report the sample mean and sample standard deviation ($c_i=1/10$) of $\epsilon_t$.

```{r}
cat('mean: ', mean(na.omit(mpq$residuals)), "\n")
cat('standard deviation: ', sd(na.omit(mpq$residuals)), "\n")
```


# 6 Step 9

TODO

## 6.1 Dataset: 

$r_t^p$ from $c_i=?$

```{r}
# prints ssr and best parameters
best_params <- select_best_model(rtp.cbest)
```

```{r}
o = capture.output(mpq <- garch(x=rtp.cbest,order=best_params))
summary(mpq)
```


### 6.1.1 

The best fitted model is GARCH(p,q) with the following estimated parameter values and standard errors.

Report the sum of the squared error of the final model.

```{r}
sum(na.omit(mpq$residuals)^2)
```


State the reason why this model is the final model, instead of GARCH(1,2),
GARCH(2,1), or GARCH(2,2).

### 6.1.2 Some diagnostic results

```{r}
shapiro.test(na.omit(residuals(mpq)))
jarque.bera.test(na.omit(residuals(mpq)))
skewness(na.omit(residuals(mpq)))
kurtosis(na.omit(residuals(mpq)))
```

```{r}
par(mfrow=c(1,2))
plot(TXT$Date[-2], rtp.cbest, type='l', xlab='Time', ylab='Log Return')
# plot fitted residuals of the best GARCH model
plot(residuals(mpq),type='h',ylab='standardized residuals')
```


Figure 6.1: The left panel is the log return original series from xx/xx/xxxx to
xx/xx/xxxx. The right panel is the fitted residuals (standardized returns or pseudo-
returns.)

```{r}
par(mfrow=c(1,2))
qqnorm(residuals(mpq)); qqline(residuals(mpq))
acf(residuals(mpq)^2,na.action=na.omit)
```


Figure 6.2: The left panel is the residual QQ plot. The right panel is the squared residual ACF plot.

1. Report the sample mean and sample standard deviation ($c_i=?$) of $\epsilon_t$.

```{r}
cat('mean: ', mean(na.omit(mpq$residuals)), "\n")
cat('standard deviation: ', sd(na.omit(mpq$residuals)), "\n")
```

# 7 Step 10

Compare results from Step 5 to Step 9. (Compare the results of the best $c_i$ and mean values.)

From Step 5 to Step 7, there are 3 distinct best c vectors (Step 8 and 9 are just using the c vector from Step 7). We see that the c_best vectors from Step 5 and Step 7 are pretty close to each other. The means are also very similar (about 0.00014). This is probably because the formula of r_t and r_t^p are very similar and both are computed through similar log returns approach.

However, the c_best for step 6 is very different from step 5 and 7, and the mean is also much larger than step 5 and 7. This c_best is actually close to (1/10,...,1/10). This is probably because of the fact that the GARCH models did not fit the data so well.








